---
title: "Archive Data on Zenodo"
author: "Eric R. Scott"
date: "`r Sys.Date()`"
output: html_document
resource_files:
- renv.lock
---

## Load Packages

```{r setup}
library(boxr)
library(httr2)
library(purrr)
library(fs)
library(glue)

box_auth_service(token_text = Sys.getenv("BOX_TOKEN_TEXT"))

## Set base URL for API requests
req_base <- 
  request("https://zenodo.org/api/") |>
  req_url_path_append("deposit", "depositions") |> 
  req_auth_bearer_token(token = Sys.getenv("ZENODO_TOKEN"))
```

## Find latest version

The DOI that links to the latest version is 10.5281/zenodo.10823037.  The numbers at the end are known as the "concept id" by Zenodo.  We can use this to find the specific deposit to create a new version of.

```{r}
concept_id <- 10823037 
concept_doi <- "10.5281/zenodo.10823037"
```

Get latest version string and record ID for this deposit

```{r}
req_concept <- 
  req_base |> 
  req_url_path("api", "deposit", "depositions") |>
  req_url_query(
    sort = "mostrecent",
    all_versions = "true",
    q = glue::glue('"query":"{concept_doi}","default_field":"conceptdoi"')
  )

resp_concept <-
  req_concept |> 
  req_perform()

concept <- resp_concept |> resp_body_json()
# Just take most recent version
latest_version <- concept[[1]]

# Double-check that concept id & DOI matches and error if it doesn't
if (latest_version$conceptdoi != "10.5281/zenodo.10823037") {
  stop("DOI of the record returned by the query isn't correct!\n",
       "Query returned ", latest_version$conceptdoi, " not ", "10.5281/zenodo.10823037")
}

# record ID of most recent version
prev_id <- latest_version[["record_id"]]
# version string of most recent version
prev_version <- latest_version[["metadata"]][["version"]]
```

Previous version: `r prev_version`

## Create record for new version
First, a new version gets created, then the data is attached to that version, then it is published.

Create the new (unpublished) version

```{r}
req_post <- 
  req_base |> 
  req_url_path_append(prev_id, "actions", "newversion") |> 
  req_method("POST")
req_post
```


```{r}
resp_new_ver <-
  req_post |> 
  req_perform()
resp_new_ver
```

Zenodo's method for attaching data is to upload it directly to a object store link returned by the above request. This gets the URL for the object store to upload data to.

```{r}
new_ver <- 
  resp_new_ver |> 
  resp_body_json()
bucket_url <- new_ver$links$bucket
new_id <- new_ver$id
```

Extract metadata from previous release, modify to update version and publication date, and attach modified version to new upload

```{r}
metadata <- 
  new_ver$metadat |> 
  list_modify(
    #Probably not best practice to use unexported functions from packages, but didn't feel like writing my own function to do this.  This increments the last number in the version string.  E.g. 1.0.1 -> 1.0.2. 
    version = usethis:::bump_version(prev_version)["patch"] |> unname(),
    publication_date = Sys.Date()
  )

```

Update metadata for new version, `r metadata$version`, published on `r metadata$publication_date`.

```{r}
req_new_meta <-
  req_base |> 
  req_method("PUT") |> 
  req_url_path_append(new_id) |> 
  req_body_json(data = list(metadata = metadata))
req_perform(req_new_meta)
```

## Attach data

Download most recent data from Box and create a temporary .zip file for upload

```{r box-dl}
dir_id <- "250527085917"
box_setwd(dir_id)
#list current files
files <- box_ls() |> as.data.frame()

#download to tempdir
dir <- fs::path_temp("gsi")
dir_create(dir)
withr::defer(dir_delete(dir)) #deletes the tempdir when this script finishes I think

walk(files$id, \(x) box_dl(x, local_dir = dir, overwrite = TRUE))
#zip the whole dir
#this is done in the temp directory so that the zip file doesn't contain nested folders of the entire file path
withr::with_dir(dir, {
  zip("gsi_data.zip", dir_ls("."))
})
zip_path <- path(dir, "gsi_data.zip")
```

Use new Zenodo API to upload file directly to object store link

```{r}
req_put <- request(bucket_url) |> 
  req_url_path_append(path_file(zip_path)) |> 
  req_auth_bearer_token(token = Sys.getenv("ZENODO_TOKEN")) |> 
  req_method("PUT") |> 
  req_body_file(zip_path)

req_put
```


```{r}
resp_put <- 
  req_put |>
  req_perform()
resp_put
```


## Publish

This makes the new version final.

```{r}
req_publish <-
  req_base |> 
  req_url_path_append(new_id, "actions", "publish") |> 
  req_method("POST")
req_publish
resp_publish <- req_publish |> req_perform()
resp_publish
```

