---
title: "Archive Data on Zenodo"
author: "Eric R. Scott"
date: "`r Sys.Date()`"
output: html_document
---

## Load Packages

```{r setup}
library(boxr)
library(httr2)
library(purrr)
library(fs)
box_auth_service(token_text = Sys.getenv("BOX_TOKEN_TEXT"))

library(jsonlite) #for testing
```

## Set base URL for API requests

```{r}
req_base <- 
  request("https://sandbox.zenodo.org/api/") |>
  req_url_path_append("deposit", "depositions") |> 
  req_auth_bearer_token(token = Sys.getenv("ZENODO_TOKEN"))
```

## Initial Release (do once only?)

### Create metadata

TODO: eventually get this metadata from an easier-to-edit YAML file?

See deposit metadata list here https://developers.zenodo.org/?python#depositions

There are many other non-required fields that may be useful


```{r}
start_version <- "1.0.0"

metadata <- list( 
  upload_type = "dataset",
  publication_date = Sys.Date(),
  #TODO: change title
  title = paste0("Green Stormwater Infrastructure Data v", start_version),
  creators = list( #TODO alternately, contributors with contributor type? Test to see if creators is required
    list(
      name = "Vanessa Buzzard",
      affiliation = "University of Arizona, School of Natural Resources and the Environment",
      orcid = "0000-0003-2929-0833"
    )#,
    # list(
    #   name = "Author 2",
    #   affiliation = "University of Arizona, department",
    #   orcid = "0000-0000-0000-0000"
    # )
  ),
  description = "This dataset is generated ...", #TODO add abstract here
  access_right = "restricted", #TODO figure out how "restricted" actually works from a users POV
  access_conditions = "Please fill out this form to request access to the data: https://forms.gle/63qWCybhvHaHunuH6",
  license = "cc-zero", #TODO choose correct license
  keywords = c("meterology", "microclimate", "campus living lab"), #TODO edit these
  version = "1.0.0" #automatic releases should only update patch, manual releases might update major or minor versions if there are changes to the structure of the data or minor bugs fixed, respectively
)
toJSON(metadata,auto_unbox = TRUE, pretty = TRUE)
```
### Create new record

```{r}
req_post <- 
  req_base |> 
  req_method("POST") |> 
  req_body_json(data = list(metadata = metadata))
req_post |> req_dry_run()
```

```{r}
resp_new_deposit <-
  req_post |> 
  req_perform()
```

```{r}
new_deposit <- 
  resp_new_deposit |> 
  resp_body_json()

```

### Attach data

Download most recent data from Box and create a .zip file for upload

```{r box-dl}
dir_id <- "250527085917"
box_setwd(dir_id)
#list current files
files <- box_ls() |> as.data.frame()

#download to tempdir
dir <- fs::path_temp()
dir_create(dir)
withr::defer(dir_delete(dir))

walk(files$id, \(x) box_dl(x, local_dir = dir, overwrite = TRUE))
#zip the whole dir
zip_path <- path(dir, "gsi_data.zip")
zip(zip_path, files = dir_ls(dir))
```

Use new Zenodo API to upload file directly to bucket link

```{r}
bucket_url <- new_deposit$links$bucket
req_put <- request(bucket_url) |> 
  req_url_path_append(path_file(zip_path)) |> 
  req_auth_bearer_token(token = Sys.getenv("ZENODO_TOKEN")) |> 
  req_method("PUT") |> 
  req_body_file(zip_path)

req_put |> req_dry_run()
```
```{r}
resp_put <- req_put |> req_perform()
resp_put |> resp_body_json()  
```

### Publish

```{r}
dep_id <- new_deposit$id
req_publish <-
  req_base |> 
  req_url_path_append(dep_id, "actions", "publish") |> 
  req_body_json(list()) |> 
  req_method("POST")
req_publish |> req_dry_run()
resp_publish <- req_publish |> req_perform()
```

## Subsequent releases

Start with existing deposit ID, keeping the metadata the same except for `publication_date` and `version`

```{r}
dep_id <- 33103
#TODO get prev version and increment
req_new_version <- 
  req_base |> 
  req_url_path_append(dep_id, "actions", "newversion") |> 
  req_body_json(list(metadata = list(
    publication_date = Sys.Date()
  ))) |> 
  req_method("POST")

resp_new_version <- req_new_version |> req_perform()
new_version <- resp_new_version |> resp_body_json()
```



```{r box-dl}
dir_id <- "250527085917"
box_setwd(dir_id)
#list current files
files <- box_ls() |> as.data.frame()

#download to tempdir
dir <- fs::path_temp()
dir_create(dir)
withr::defer(dir_delete(dir))

walk(files$id, \(x) box_dl(x, local_dir = dir, overwrite = TRUE))
#zip the whole dir
zip_path <- path(dir, "gsi_data.zip")
zip(zip_path, files = dir_ls(dir))
```
```{r}
bucket_url <- new_version$links$bucket
req_put <- request(bucket_url) |> 
  req_url_path_append(path_file(zip_path)) |> 
  req_auth_bearer_token(token = Sys.getenv("ZENODO_TOKEN")) |> 
  req_method("PUT") |> 
  req_body_file(zip_path)

req_put |> req_dry_run()
req_put |> req_perform()
```

```{r}
req_publish <-
  req_base |> 
  req_url_path_append(new_version$id, "actions", "publish") |> 
  req_body_json(list()) |> 
  req_method("POST")
req_publish |> req_dry_run()
resp_publish <- req_publish |> req_perform()
resp_publish
```

